Dissertation Proposal

### 2023-10-25 paper.tex
fix references
clean up tables

\bibliography{bibfile}

\usepackage{geometry} % Adjust page margins
\usepackage{amsmath, amssymb} % For math symbols and equations
\usepackage{graphicx} % For including images
\usepackage{titlesec} % For customizing section titles
\usepackage{biblatex} % For managing references
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\miscon}[1]{\textbf{#1}}
\newcommand{\surmisedMiscon}[1]{\miscon{#1}$^\ddag$}
\newcommand{\pValue}[0]{\textit{p}\nobreakdash-value}

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{tabularx}   %% For tables with growable column
\usepackage{cleveref}   %% For smart ref
\usepackage{graphicx}   %% For inserting images
\graphicspath{ {./images/} }  %% configure the graphicx package
\usepackage{multirow}
\usepackage{multicol}
\usepackage{ragged2e}  %% For \raggedright
\usepackage{listings}  %% For typesetting code
\usepackage{enumitem}  %% For noitemsep and topsep
\lstdefinelanguage{smol} {
  alsoletter={ABCDEFGHIJKLMNOPQRSTUVWXYZabcdefghijklmnopqrstuvwxyz-!?*},
  morekeywords={defvar,deffun,lambda,set!,let,let*,letrec,begin,if,cond,else,and,or},
  morecomment=[l]{;},
  morestring=[b]",
}
\lstset{
  basicstyle=\small\ttfamily,
  breaklines=true,
  language=smol,
  % aboveskip=-0.3 \baselineskip,   % remove extra space before
  % belowskip=-0.8 \baselineskip,     % and after code blocks
}
%% Custom commands:
%% new terms are introduced with a boldface
%% (the common style is italic, but KC thinks bf is easier to locate)
\newcommand{\newterm}[1]{\textbf{#1}}

@@

\begin{document}

@@

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l l}
    \textbf{Questions}                       &
    \textbf{Frequency Table of Answers}          \\\hline
    \lstinputlisting{programs/def_twice.txt} & {
        \begin{tabularx}{1in}{r l}
          $^\dag$59\%  & \verb|2 0|             \\
          *32\% & \verb|Error|           \\
          4\%   & \verb|Other: 2 2|      \\
          3\%   & ``Nothing is printed'' \\
          2\%   & \verb|0 0|             \\
        \end{tabularx}
    }                                            \\\hline
    \lstinputlisting{programs/dyn_scope.txt} & {
        \begin{tabularx}{1in}{r l}
          *65\% & \verb|Error| \\
          $^\dag$29\%  & \verb|42 #t| \\
          6\%   & Other        \\
        \end{tabularx}
    }                                            \\\hline
    \lstinputlisting{programs/reassign.txt}  & {
        \begin{tabularx}{1in}{r l}
          *53\% & \verb|#(6 5) 5|                 \\
          *20\% & \verb|Error|                    \\
          $^\dag$11\%  & \verb|#(6 6) 5|                 \\
          $^\dag$11\%  & \verb|#(6 6) 6|                 \\
          5\%   & ``Nothing is printed'' or Other \\
        \end{tabularx}
    }                                            \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizFun. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that we discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-fun}
\end{table}
\Cref{t:quizzes-data-fun} lists programs in \quizFun{} that we
consider the most interesting. These data confirm the presence of
scope-related misconceptions:
\begin{enumerate}
  \item At least 59\% of students incorrectly believe that a
        variable can be defined twice in one block.
  \item 29\% of students believe that a variable defined in a function
        will be available in the top-level (or global) environment
        after the function is called. That is, these students may have a
        dynamic scope misconception.
  \item 22\% (11\% + 11\%) of students believe variables themselves
        can be passed as arguments and redefined inside the function.
        They disagree on whether the redefinition persists after the
        function call.
\end{enumerate}

@@

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l l}
    \textbf{Question}                           &
    \textbf{Frequency Table of Answers}             \\\hline
    \lstinputlisting{programs/circularity.txt}  & {
        \begin{tabularx}{1in}{r p{2.5in}}
          $^\dag$50\%  & \verb|#(#(2 #(2 3)) #(2 3))| \\
          *29\% & \verb|x=#(x x)| or
          something similar. Both \verb|(left x)| and \verb|(right x)|
          are \verb|x| itself.                 \\
          $^\dag$16\%  & \verb|Error|                 \\
          5\%   & Other                        \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/mvec_in_mvec.txt} & {
        \begin{tabularx}{1in}{r p{2.5in}}
          *62\% & \verb|#(#(100 2 3 4) #(100 2 3 4))| \\
          $^\dag$26\%  & \verb|#(#(1 2 3 4) #(100 2 3 4))|   \\
          6\%   & \texttt{Error}                      \\
          4\%   & \verb|#(#(1 2 3 4) #(1 2 3 4))|     \\
          2\%   & Other                               \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/vset_in_let.txt}  & {
        \begin{tabularx}{1in}{r p{2.5in}}
          *59\% & \verb|#(10)|  \\
          $^\dag$36\%  & \verb|#(123)| \\
          5\%   & Other         \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/var_as_arg.txt}   & {
        \begin{tabularx}{1in}{r p{2.5in}}
          *65\% & \texttt{12} \\
          $^\dag$31\%  & \texttt{0}  \\
          4\%   & Other       \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/setset.txt}       & {
        \begin{tabularx}{1in}{r p{2.5in}}
          *59\% & Other: \texttt{5 7}   \\
          $^\dag$27\% & \texttt{6 7}          \\
          11\%  & \texttt{5 5}          \\
          2\%  & Other: \texttt{Error} \\
          1\%  & Other: \texttt{5 6}   \\
        \end{tabularx}
    }                                               \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizState. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that we discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-state}
\end{table}
\Cref{t:quizzes-data-state} lists interesting programs after the
addition of state. These data suggest the students have aliasing-related misconceptions:
\begin{itemize}
  \item Up to 50\% of students think vectors are copied rather than
  aliased.
  \item 16\% of students think trying to construct and print a
  self-referring vector would error. (This program is ambiguous:
  \emph{constructing} works in most SMoL languages, but \emph{printing}
  may well cause a problem. These identified ambiguities are
  addressed in \Cref{s:tutor-refine-program-set}.)
  \item 31\% of students think a variable is aliased by a parameter if
        the two variables have the same name. Perhaps interestingly,
        fewer students (27\%) think the variable aliasing would
        happen if the two variables had different names.
\end{itemize}

@@

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l l}
    \textbf{Question}                                 &
    \textbf{Frequency Table of Answers}                   \\\hline
    \lstinputlisting{programs/fun_returns_lambda.txt} & {
        \begin{tabularx}{1in}{r p{2.5in}}
          *82\% & \verb|3|     \\
          $^\dag$17\%  & \verb|Error| \\
          1\%   & Other        \\
        \end{tabularx}
    }                                                     \\\hline
    \lstinputlisting{programs/fun_and_state_1.txt}    & {
        \begin{tabularx}{1in}{r p{2.5in}}
          *74\% & \verb|4|            \\
          $^\dag$21\%  & \verb|3|            \\
          6\%   & Other: \verb|Error| \\
        \end{tabularx}
    }                                                     \\\hline
    \lstinputlisting{programs/fun_and_state_2.txt}    & {
        \begin{tabularx}{1in}{r p{2.5in}}
          *88\% & \verb|4|            \\
          $^\dag$10\%  & \verb|3|            \\
          3\%   & Other: \verb|Error| \\
        \end{tabularx}
    }                                                     \\\hline
    \lstinputlisting{programs/counter.txt}            & {
        \begin{tabularx}{1in}{r p{2.5in}}
          *62\% & \verb|1 1 2 3 2| \\
          $^\dag$34\%  & \verb|1 1 1 1 1| \\
          4\%   & Other            \\
          1\%   & \verb|1 1 2 3 4| \\
        \end{tabularx}
    }                                                     \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizHof. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that we discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-hof}
\end{table}
\Cref{t:quizzes-data-hof} lists interesting programs
after the addition of closures and higher-order functions.
It extends what we saw with loops in
\Cref{s:intro}: that students have misconceptions about their interaction with mutable variables:
\begin{itemize}
  \item 17\% of students think \texttt{lambda} functions can't refer
        to free variables.
  \item 21\% of the students think mutating a variable defined outside
        a lambda can't possibly change the behavior of the lambda.
        Perhaps interestingly, this
        misconception seems to depend on how the lambda is constructed
        (compare the middle two programs).
  \item Student understanding of the
        \lstinline|let|-over-\lstinline|lambda| pattern is weak.
\end{itemize}

@@

  \begin{table}[t]
    \centering
    \begin{tabularx}{\linewidth}{m{0.3\textwidth} l l}
      \textbf{Misconception}                                                     &
      \textbf{Question}                                                          &
      \textbf{Table of Answers}
      \\\hline
      \miscon{CallByRef} Function calls alias variables.                         &
       % mut-vars.not_aliased_by_funarg_2 (35)
       \lstinputlisting{programs/call-by-ref.txt}                                                                    & {
        \begin{tabularx}{1in}{r l}
          78\%  & \verb|12|      \\
          11\% & \verb|error|      \\
          **10\%   & \verb|0|  \\
          1\%   & \verb|23|  \\
        \end{tabularx}
    }
      \\\hline
      \miscon{CallsCopyStructs} Function calls copy data structures.      &
      % vectors2.alias_with_funcall (48)
      \lstinputlisting{programs/calls-copy-structs.txt}
      & {
        \begin{tabularx}{1in}{r l}
          90\%  & \verb|#(173 0)|      \\
          **10\%   & \verb|#(1 0)|  \\
        \end{tabularx}
    } \\\hline
      \miscon{DeepClosure} Closures copy the \textit{values} of free variables.  &
      % lambda3.lambda_remembers_env (70)
      \lstinputlisting{programs/deep-closure.txt}                                & {
          \begin{tabularx}{1in}{r l}
            86\%  & \verb|4|      \\
            **10\% & \verb|3|      \\
            3\%   & \verb|error|  \\
            1\%   & \verb|lambda| \\
          \end{tabularx}
      }                                                                                   \\\hline
      \miscon{DefByRef} Variable definitions alias variables.                    &
      % mut-vars.not_aliased_by_defvar_1 (29)
      \lstinputlisting{programs/def-by-ref.txt}                                  & {
          \begin{tabularx}{1in}{r p{0.2\textwidth}}
            85\%   & \verb|0 12|                \\
            **12\% & \verb|0 0|                 \\
            2\%    & \verb|error|               \\
            1\%    & depends on implementation. \\
          \end{tabularx}
        }
      \\\hline
      \miscon{DefOrSet}  Both definitions and variable assignments are
      interpreted as follows: if a variable is not defined in the
      current environment, it is defined. Otherwise, it is mutated to
      the new value.
      &
      % program: mut-vars.update_undefined (28)
      \lstinputlisting{programs/def-or-set.txt}                                  & {
          \begin{tabularx}{1in}{r l}
            85\%   & \verb|error| \\
            **15\% & \verb|2|     \\
          \end{tabularx}
        }
      \\\hline
      \miscon{DefsCopyStructs} Variable definitions copy structures recursively. &
      % vectors2.alias_with_defvar (47)
      \lstinputlisting{programs/defs-copy-structs.txt}                                & {
          \begin{tabularx}{1in}{r l}
            **67\% & \verb|#(100)| \\
            30\%   & \verb|#(200)| \\
            1\%    & \verb|#(300)| \\
            1\%    & \verb|error|  \\
          \end{tabularx}
      }                                                                                   \\\hline
    \end{tabularx}
    \caption{Ground misconceptions identified by the SMoL~Tutor. Answers marked
      with ``**'' represent the misconception. (Part I)}
    \label{t:tutor-grounded-misconceptions-1}
  \end{table}

@@

>>>>

\usepackage[utf8]{inputenc} % Use UTF-8 encoding
\usepackage[T1]{fontenc} % Use the T1 font encoding
\usepackage{geometry} % Adjust page margins
\usepackage{amsmath, amssymb} % For math symbols and equations
\usepackage{graphicx} % For including images
\usepackage{titlesec} % For customizing section titles
\usepackage[style=authoryear]{biblatex}  % For managing references
\addbibresource{bibfile.bib}
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\miscon}[1]{\textbf{#1}}
\newcommand{\surmisedMiscon}[1]{\miscon{#1}$^\ddag$}
\newcommand{\pValue}[0]{\textit{p}\nobreakdash-value}

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{tabularx}   %% For tables with growable column
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\usepackage{cleveref}   %% For smart ref
\usepackage{graphicx}   %% For inserting images
\graphicspath{ {./images/} }  %% configure the graphicx package
\usepackage{multirow}
\usepackage{multicol}
\usepackage{ragged2e}  %% For \raggedright
\usepackage{listings}  %% For typesetting code
\usepackage{enumitem}  %% For noitemsep and topsep
\lstdefinelanguage{smol} {
  alsoletter={ABCDEFGHIJKLMNOPQRSTUVWXYZabcdefghijklmnopqrstuvwxyz-!?*},
  morekeywords={defvar,deffun,lambda,set!,let,let*,letrec,begin,if,cond,else,and,or},
  morecomment=[l]{;},
  morestring=[b]",
}
\lstset{
  basicstyle=\small\ttfamily,
  breaklines=true,
  language=smol,
  % aboveskip=-0.3 \baselineskip,   % remove extra space before
  % belowskip=-0.8 \baselineskip,     % and after code blocks
}
%% Custom commands:
%% new terms are introduced with a boldface
%% (the common style is italic, but KC thinks bf is easier to locate)
\newcommand{\newterm}[1]{\textbf{#1}}

@@

\begin{document}
\maketitle

@@

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l X}
    \textbf{Questions}                       &
    \textbf{Table of Answers}          \\\hline
    \lstinputlisting{programs/def_twice.txt} & {
        \begin{tabularx}{\linewidth}{r X}
          $^\dag$59\%  & \verb|2 0|             \\
          *32\% & \verb|Error|           \\
          4\%   & \verb|Other: 2 2|      \\
          3\%   & ``Nothing is printed'' \\
          2\%   & \verb|0 0|             \\
        \end{tabularx}
    }                                            \\\hline
    \lstinputlisting{programs/dyn_scope.txt} & {
        \begin{tabularx}{\linewidth}{r X}
          *65\% & \verb|Error| \\
          $^\dag$29\%  & \verb|42 #t| \\
          6\%   & Other        \\
        \end{tabularx}
    }                                            \\\hline
    \lstinputlisting{programs/reassign.txt}  & {
        \begin{tabularx}{\linewidth}{r X}
          *53\% & \verb|#(6 5) 5|                 \\
          *20\% & \verb|Error|                    \\
          $^\dag$11\%  & \verb|#(6 6) 5|                 \\
          $^\dag$11\%  & \verb|#(6 6) 6|                 \\
          5\%   & ``Nothing is printed'' or Other \\
        \end{tabularx}
    }                                            \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizFun. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that we discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-fun}
\end{table}
\Cref{t:quizzes-data-fun} lists programs in \quizFun{} that we
consider the most interesting. These data confirm the presence of
scope-related misconceptions:
\begin{enumerate}
  \item At least 59\% of students incorrectly believe that a
        variable can be defined twice in one block.
  \item 29\% of students believe that a variable defined in a function
        will be available in the top-level (or global) environment
        after the function is called. That is, these students may have a
        dynamic scope misconception.
  \item 22\% (11\% + 11\%) of students believe variables themselves
        can be passed as arguments and redefined inside the function.
        They disagree on whether the redefinition persists after the
        function call.
\end{enumerate}

@@

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l X}
    \textbf{Question}                           &
    \textbf{Table of Answers}             \\\hline
    \lstinputlisting{programs/circularity.txt}  & {
        \begin{tabularx}{\linewidth}{r X}
          $^\dag$50\%  & \verb|#(#(2 #(2 3)) #(2 3))| \\
          *29\% & \verb|x=#(x x)| or
          something similar. Both \verb|(left x)| and \verb|(right x)|
          are \verb|x| itself.                 \\
          $^\dag$16\%  & \verb|Error|                 \\
          5\%   & Other                        \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/mvec_in_mvec.txt} & {
        \begin{tabularx}{\linewidth}{r X}
          *62\% & \verb|#(#(100 2 3 4) #(100 2 3 4))| \\
          $^\dag$26\%  & \verb|#(#(1 2 3 4) #(100 2 3 4))|   \\
          6\%   & \texttt{Error}                      \\
          4\%   & \verb|#(#(1 2 3 4) #(1 2 3 4))|     \\
          2\%   & Other                               \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/vset_in_let.txt}  & {
        \begin{tabularx}{\linewidth}{r X}
          *59\% & \verb|#(10)|  \\
          $^\dag$36\%  & \verb|#(123)| \\
          5\%   & Other         \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/var_as_arg.txt}   & {
        \begin{tabularx}{\linewidth}{r X}
          *65\% & \texttt{12} \\
          $^\dag$31\%  & \texttt{0}  \\
          4\%   & Other       \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/setset.txt}       & {
        \begin{tabularx}{\linewidth}{r X}
          *59\% & Other: \texttt{5 7}   \\
          $^\dag$27\% & \texttt{6 7}          \\
          11\%  & \texttt{5 5}          \\
          2\%  & Other: \texttt{Error} \\
          1\%  & Other: \texttt{5 6}   \\
        \end{tabularx}
    }                                               \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizState. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that we discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-state}
\end{table}
\Cref{t:quizzes-data-state} lists interesting programs after the
addition of state. These data suggest the students have aliasing-related misconceptions:
\begin{itemize}
  \item Up to 50\% of students think vectors are copied rather than
  aliased.
  \item 16\% of students think trying to construct and print a
  self-referring vector would error. (This program is ambiguous:
  \emph{constructing} works in most SMoL languages, but \emph{printing}
  may well cause a problem. These identified ambiguities are
  addressed in \Cref{s:tutor-refine-program-set}.)
  \item 31\% of students think a variable is aliased by a parameter if
        the two variables have the same name. Perhaps interestingly,
        fewer students (27\%) think the variable aliasing would
        happen if the two variables had different names.
\end{itemize}

@@

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l X}
    \textbf{Question}                                 &
    \textbf{Table of Answers}                   \\\hline
    \lstinputlisting{programs/fun_returns_lambda.txt} & {
        \begin{tabularx}{\linewidth}{r X}
          *82\% & \verb|3|     \\
          $^\dag$17\%  & \verb|Error| \\
          1\%   & Other        \\
        \end{tabularx}
    }                                                     \\\hline
    \lstinputlisting{programs/fun_and_state_1.txt}    & {
        \begin{tabularx}{\linewidth}{r X}
          *74\% & \verb|4|            \\
          $^\dag$21\%  & \verb|3|            \\
          6\%   & Other: \verb|Error| \\
        \end{tabularx}
    }                                                     \\\hline
    \lstinputlisting{programs/fun_and_state_2.txt}    & {
        \begin{tabularx}{\linewidth}{r X}
          *88\% & \verb|4|            \\
          $^\dag$10\%  & \verb|3|            \\
          3\%   & Other: \verb|Error| \\
        \end{tabularx}
    }                                                     \\\hline
    \lstinputlisting{programs/counter.txt}            & {
        \begin{tabularx}{\linewidth}{r X}
          *62\% & \verb|1 1 2 3 2| \\
          $^\dag$34\%  & \verb|1 1 1 1 1| \\
          4\%   & Other            \\
          1\%   & \verb|1 1 2 3 4| \\
        \end{tabularx}
    }                                                     \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizHof. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that we discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-hof}
\end{table}
\Cref{t:quizzes-data-hof} lists interesting programs
after the addition of closures and higher-order functions.
It extends what we saw with loops in
\Cref{s:intro}: that students have misconceptions about their interaction with mutable variables:
\begin{itemize}
  \item 17\% of students think \texttt{lambda} functions can't refer
        to free variables.
  \item 21\% of the students think mutating a variable defined outside
        a lambda can't possibly change the behavior of the lambda.
        Perhaps interestingly, this
        misconception seems to depend on how the lambda is constructed
        (compare the middle two programs).
  \item Student understanding of the
        \lstinline|let|-over-\lstinline|lambda| pattern is weak.
\end{itemize}

@@

  \begin{table}[t]
    \centering
    \begin{tabularx}{\textwidth}{m{0.25\textwidth} l Y}
      \textbf{Misconception}                                                     &
      \textbf{Question}                                                          &
      \textbf{Table of Answers}
      \\\hline
      \miscon{CallByRef} Function calls alias variables.                         &
       % mut-vars.not_aliased_by_funarg_2 (35)
       \lstinputlisting{programs/call-by-ref.txt}                                                                    & {
        \begin{tabularx}{1in}{r l}
          78\%  & \verb|12|      \\
          11\% & \verb|error|      \\
          **10\%   & \verb|0|  \\
          1\%   & \verb|23|  \\
        \end{tabularx}
    }
      \\\hline
      \miscon{CallsCopyStructs} Function calls copy data structures.      &
      % vectors2.alias_with_funcall (48)
      \lstinputlisting{programs/calls-copy-structs.txt}
      & {
        \begin{tabularx}{1in}{r l}
          90\%  & \verb|#(173 0)|      \\
          **10\%   & \verb|#(1 0)|  \\
        \end{tabularx}
    } \\\hline
      \miscon{DeepClosure} Closures copy the \textit{values} of free variables.  &
      % lambda3.lambda_remembers_env (70)
      \lstinputlisting{programs/deep-closure.txt}                                & {
          \begin{tabularx}{1in}{r l}
            86\%  & \verb|4|      \\
            **10\% & \verb|3|      \\
            3\%   & \verb|error|  \\
            1\%   & \verb|lambda| \\
          \end{tabularx}
      }                                                                                   \\\hline
      \miscon{DefByRef} Variable definitions alias variables.                    &
      % mut-vars.not_aliased_by_defvar_1 (29)
      \lstinputlisting{programs/def-by-ref.txt}                                  & {
          \begin{tabularx}{1in}{r Y}
            85\%   & \verb|0 12|                \\
            **12\% & \verb|0 0|                 \\
            2\%    & \verb|error|               \\
            1\%    & depends on implementation. \\
          \end{tabularx}
        }
      \\\hline
      \miscon{DefOrSet}  Both definitions and variable assignments are
      interpreted as follows: if a variable is not defined in the
      current environment, it is defined. Otherwise, it is mutated to
      the new value.
      &
      % program: mut-vars.update_undefined (28)
      \lstinputlisting{programs/def-or-set.txt}                                  & {
          \begin{tabularx}{1in}{r l}
            85\%   & \verb|error| \\
            **15\% & \verb|2|     \\
          \end{tabularx}
        }
      \\\hline
      \miscon{DefsCopyStructs} Variable definitions copy structures recursively. &
      % vectors2.alias_with_defvar (47)
      \lstinputlisting{programs/defs-copy-structs.txt}                                & {
          \begin{tabularx}{1in}{r l}
            **67\% & \verb|#(100)| \\
            30\%   & \verb|#(200)| \\
            1\%    & \verb|#(300)| \\
            1\%    & \verb|error|  \\
          \end{tabularx}
      }                                                                                   \\\hline
    \end{tabularx}
    \caption{Ground misconceptions identified by the SMoL~Tutor. Answers marked
      with ``**'' represent the misconception. (Part I)}
    \label{t:tutor-grounded-misconceptions-1}
  \end{table}

@@

\section{References}

\printbibliography
